### 2021-03-12 results/draft.tex
added the second paragraph (weakness of previous approaches)

\ \ \ \ \ \ \ \ \ \ 
One step towards overcoming these uncertainties is a understanding of the "ecology of eDNA":  (Barnes \& Turner 2016). Previous studies

>>>>

\ \ \ \ \ \ \ \ \ \ 
After the suggestion of the importance to understand about origin, state, transport, and fate of eDNA ("ecology of eDNA") by Barnes \& Turner (2016), the studies which used laboratory experiments and numerical hydrological models have been increased to overcome the uncertainty of eDNA. 
%To overcome the uncertainty of eDNA, the studies which used Laboratory experiments and numerical hydrological models have been increased after suggested the importance to understand about origin, state, transport, and fate of eDNA ("ecology of eDNA") by Barnes \& Turner (2016).
%Laboratory experiments and numerical hydrological models have been used to overcome the uncertainty of eDNA, because Barnes \& Turner (2016) suggested the importance of knowledge about origin, state, transport, and fate of eDNA ("ecology of eDNA").  
% Laboratory experiments and numerical hydrological models have been used to overcome the uncertainty of eDNA, especially after suggested the importance of "ecology of eDNA" by Barnes \& Turner (2016).
For example, the relationship between production rate of eDNA and biological factors (e.g., species and body mass) or environmental factors (e.g., temperature), and between decomposition of eDNA and the sate of eDNA (e.g., length of eDNA) or environmental factors were measured. In numerical hydrological models, spatial distribution of eDNA was simulated in aquatic area and obtain the production, transport and decay of eDNA (e.g., Fukaya et al. 2020). %深谷さんの論文に引用あり
However, the keep for all focal species in laboratory is not realistic and low cost-efficiency when multi species studies such as biodiversity monitoring and fisheries management. Moreover, biologists monitoring species are often not familiar with hydrological models and the simulation of eDNA often seems to be hard for them.
